R Notebook for MSDepression Project

### 2021-01-26 dac_summary.Rmd
Add files via upload

---
title: "Dac Summary"
output:
  html_document
---

@@

#set data_empi_acc_f_phq to data3
data_empi_acc_f_phq <- data3#subset(data, select = c("EMPI", "ACCESSION_NUM", "PHQ.2", "PHQ.9"))

@@

#number of unique in my group
eb_access_n <- length(unique(data_empi_acc_f_phq$ACCESSION_NUM)) #n = 21027

@@

melissa_peeps_in_eb_group <- sum(unique(melissa_xls$ACCESSION_NUM) %in% unique(data_empi_acc_f_phq$ACCESSION_NUM)) #n = 15137

@@

eb_peeps_in_melissa_group <- sum(unique(data_empi_acc_f_phq$ACCESSION_NUM) %in% unique(melissa_xls$ACCESSION_NUM)) #n=15137

@@

#make accession # and lab findings into integer type, contained in row 28:42, Margin=2 to work on columns
data_empi_acc_f_phq$ACCESSION_NUM <- as.integer(data_empi_acc_f_phq$ACCESSION_NUM)
data_empi_acc_f_phq[28:42] <- apply(X = data_empi_acc_f_phq[28:42], FUN = as.integer, MARGIN = 2)
data_empi_acc_f_phq$sex_binarized <- ifelse(data_empi_acc_f_phq$SEX == "MALE", 1, 2)
data_empi_acc_f_phq$race_binarized <- ifelse(data_empi_acc_f_phq$RACE == "WHITE", 1, 2)

@@

#f-codes - people usually have BOTH icd9/10 or neither
num_depression <- length(which(!is.na(data_empi_acc_f_phq$ICD9))) #n=11131
print(paste0("N with ICD 9/10 codes for depression = ", num_depression))

num_unique_EMPI_and_dep <- length(which(!is.na(data_empi_acc_f_phq$ICD9) & unique(data_empi_acc_f_phq$EMPI))) #n = 593
print(paste0("N with ICD 9/10 codes for depression and unique EMPI = ", num_unique_EMPI_and_dep))

num_phq2_and_dep <- length(which(!is.na(data_empi_acc_f_phq$ICD9) & !is.na(data_empi_acc_f_phq$PHQ.2))) #n = 4855
print(paste0("N with ICD 9/10 codes for depression and phq2 = ", num_phq2_and_dep))

num_phq9_and_dep <- length(which(!is.na(data_empi_acc_f_phq$ICD9) & !is.na(data_empi_acc_f_phq$PHQ.9))) #n=669
print(paste0("N with ICD 9/10 codes for depression and phq9 = ", num_phq9_and_dep))

#fcode histos
hist(data_empi_acc_f_phq$PHQ.2[which(!is.na(data_empi_acc_f_phq$ICD9) & !is.na(data_empi_acc_f_phq$PHQ.2))], 
     main = paste0("PHQ2 and Dep Histo : n = ", length(which(!is.na(data_empi_acc_f_phq$ICD9) & !is.na(data_empi_acc_f_phq$PHQ.2)))), xlab = paste0("PHQ2"))

hist(data_empi_acc_f_phq$PHQ.9[which(!is.na(data_empi_acc_f_phq$ICD9) & !is.na(data_empi_acc_f_phq$PHQ.9))], 
     main = paste0("PHQ9 and Dep Histo : n = ", length(which(!is.na(data_empi_acc_f_phq$ICD9) & !is.na(data_empi_acc_f_phq$PHQ.9)))), xlab = paste0("PHQ9"))

@@

#########################
### Erica's group  ####
#########################
data_e <- data3

@@

#remove people who do not have phq2 or 9
data_e_with_phq2 <- data_e[which(!is.na(data_e$PHQ.2)),] #4864
data_e_with_phq9 <- data_e[which(!is.na(data_e$PHQ.9)),] #376

@@

>>>>

---
title: "Dac Summary"
output:
  html_document: default
  pdf_document: default
---

@@

#from Jan 2021 pull
data4_20210119 <- read.csv("/Users/eballer/BBL/msdepression/data/dac/investigatingdepressioninmspatients.csv", header = TRUE, stringsAsFactors = FALSE, na.strings = c("NULL"), sep =",")

#set data_empi_acc_f_phq to data4
data_empi_acc_f_phq <- data4_20210119#subset(data, select = c("EMPI", "ACCESSION_NUM", "PHQ.2", "PHQ.9"))

@@

#number of unique in my group
eb_access_n <- length(unique(data_empi_acc_f_phq$ACCESSION_NUM)) #n = 21027 -42840

@@

melissa_peeps_in_eb_group <- sum(unique(melissa_xls$ACCESSION_NUM) %in% unique(data_empi_acc_f_phq$ACCESSION_NUM)) #n = 15137 -> 25857

@@

eb_peeps_in_melissa_group <- sum(unique(data_empi_acc_f_phq$ACCESSION_NUM) %in% unique(melissa_xls$ACCESSION_NUM)) #n=15137 -> 25857

@@

#make accession # and lab findings into integer type, contained in row 28:42, Margin=2 to work on columns
data_empi_acc_f_phq$ACCESSION_NUM <- as.integer(data_empi_acc_f_phq$ACCESSION_NUM)
data_empi_acc_f_phq[27:29] <- apply(X = data_empi_acc_f_phq[27:29], FUN = as.integer, MARGIN = 2)
data_empi_acc_f_phq[31:45] <- apply(X = data_empi_acc_f_phq[31:45], FUN = as.integer, MARGIN = 2)
data_empi_acc_f_phq$sex_binarized <- ifelse(data_empi_acc_f_phq$SEX == "MALE", 1, 2)
data_empi_acc_f_phq$race_binarized <- ifelse(data_empi_acc_f_phq$RACE == "WHITE", 1, 2)

@@

#f-codes - people usually have BOTH icd9/10 or neither
#num_depression <- length(which(!is.na(data_empi_acc_f_phq$ICD9))) #n=11131
num_depression <- length(grep("F3", data_empi_acc_f_phq$ICD10))
print(paste0("N with ICD 9/10 codes for depression = ", num_depression))

#num_unique_EMPI_and_dep <- length(which(!is.na(data_empi_acc_f_phq$ICD9) & unique(data_empi_acc_f_phq$EMPI))) #n = 593
# compares overlap of # people with F3* ICD 10 and the unique EMPIs
#depression df
dep_df <- grep("F3", data_empi_acc_f_phq$ICD10)
unique_empi <- match(unique(data_empi_acc_f_phq$EMPI), data_empi_acc_f_phq$EMPI)
num_unique_EMPI_and_dep <- sum(unique_empi %in% dep_df) #n = 6386

print(paste0("N with ICD 9/10 codes for depression and unique EMPI = ", num_unique_EMPI_and_dep))

num_phq2_and_dep <- sum(dep_df %in% which(!is.na(data_empi_acc_f_phq$PHQ.2))) #n = 6295
print(paste0("N with ICD 9/10 codes for depression and phq2 = ", num_phq2_and_dep))

num_phq9_and_dep <- sum(dep_df %in% which(!is.na(data_empi_acc_f_phq$PHQ.9))) #n=932
print(paste0("N with ICD 9/10 codes for depression and phq9 = ", num_phq9_and_dep))

#fcode histos
hist(data_empi_acc_f_phq$PHQ.2[dep_df %in% which(!is.na(data_empi_acc_f_phq$PHQ.2))], 
     main = paste0("PHQ2 and Dep Histo : n = ", num_phq2_and_dep), xlab = paste0("PHQ2"))

hist(data_empi_acc_f_phq$PHQ.9[dep_df %in% which(!is.na(data_empi_acc_f_phq$PHQ.9))], 
     main = paste0("PHQ2 and Dep Histo : n = ", num_phq9_and_dep), xlab = paste0("PHQ9"))

@@

#########################
### Erica's group  ####
#########################
data_e <- data4_20210119

@@

#remove people who do not have phq2 or 9
data_e_with_phq2 <- data_e[which(!is.na(data_e$PHQ.2)),] #13820
data_e_with_phq9 <- data_e[which(!is.na(data_e$PHQ.9)),] #1202

@@

################################
#### Subset by MS Attending ####
################################

#obtained from: unique(data_empi_acc_f_phq$Provider[grep("PRUIT", data_empi_acc_f_phq$Provider)])
ms_providers <- c("MARKOWITZ, CLYDE E.", "JACOBS, LINDA", "WILLIAMSON, ERIC MICHAEL-LEE", "BERGER, JOSEPH ROBERT", "BERGER DO, JOSEPH", "PRUITT, AMY A.", "KOLSON, DENNIS L.", "CHAHIN, SALIM", "NARULA, SONA", "BAR-OR, AMIT")

#repeat demographics with only those w/MS providers

data_e <- data4_20210119[which(data_empi_acc_f_phq$Provider %in% ms_providers),]
dep_df <- grep("F3", data_e$ICD10)
unique_empi <- match(unique(data_e$EMPI), data_e$EMPI)
num_unique_EMPI_and_dep <- sum(unique_empi %in% dep_df) #n = 469

#remove people who do not have phq2 or 9
data_e_with_phq2 <- data_e[which(!is.na(data_e$PHQ.2)),] #13820
data_e_with_phq9 <- data_e[which(!is.na(data_e$PHQ.9)),] #1202

print(paste0("This looks at data set that only includes people with MS PROVIDERS:"))
print(paste0(ms_providers))

#unique accession #s
print(paste0("Number of unique accession #s n= ", length(unique(data_e$ACCESSION_NUM))))

#dep_df includes anyone with ICD 9/10 codes for depression.
print(paste0("N with ICD 9/10 codes for depression and phq2- ", sum(!is.na(data_e[dep_df,]$PHQ.2))))
print(paste0("N with ICD 9/10 codes for depression and phq9- ", sum(!is.na(data_e[dep_df,]$PHQ.9))))

print(paste0("N with ICD 9/10 codes for depression and unique EMPI = ", num_unique_EMPI_and_dep))

print(paste0("N PHQ2 = ", sum(!is.na(data_e$PHQ.2)), " out of ", dim(data_e)[1]))

print(paste0("N PHQ9 = ", sum(!is.na(data_e$PHQ.9)), " out of ", dim(data_e)[1]))

print(paste0("N in EB group w/phq2 = ", sum(!is.na(data_e_no_duplicate_EMPI$PHQ.2)), " out of ", dim(data_e)[1])) #

print(paste0("N in EB group w/phq9 = ", sum(!is.na(data_e_no_duplicate_EMPI$PHQ.9)), " out of ", dim(data_e)[1])) #

### 2021-01-26 lab_notebook.Rmd
Add files via upload

>>>>

#### 20210126

A lot of success. Went back and forth with DAC, decided to ask for basically everyone, and we would post sort for providers that were associated with MS clinic, assuming that patients who received a diagnosis of MS from one of these people actually had it.

Updates dac_summary to include not only a summary of the returned DAC pull, but also of the subset of people with MS providers. dac_summary.Rmd can be found on github, and summary table on: https://docs.google.com/presentation/d/1pDWXYUmq6sq7Xe08HaWdxLELa-qtQtABCw8RIIZ_7to/edit#slide=id.gb446eacf6a_0_0
